Finite-state morphological transducers for three Kypchak languages

### 2014-03-23 kipchak-lrec-2013/kipchak-paper.tex
minor wording and spacing fixes
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@51112 72bbbca6-d526-0410-a7d9-f06f51895060

This paper overviews the languages (§\ref{sec:lgs}), provides background on these morphological transducers and related previous work (§\ref{sec:bg}), describes the development effort and contents of the transducers (§\ref{sec:methodology}), evaluates the effectiveness of these transducers (§\ref{sec:evaluation}), and summarises the findings (§\ref{sec:conclusions}).

@@

Our solution for these consistent exceptions is to make a separate continuation lexicon for e.g., Russian nouns.  This continuation lexicon adds a character that the phonology deletes, but that triggers phonological rules.

>>>>

This paper gives an overview of the languages (§\ref{sec:lgs}), provides background on these morphological transducers and related previous work (§\ref{sec:bg}), describes the development effort and contents of the transducers (§\ref{sec:methodology}), evaluates the effectiveness of these transducers (§\ref{sec:evaluation}), and summarises the findings (§\ref{sec:conclusions}).

@@

Our solution for these consistent exceptions is to make a separate continuation lexicon for e.g., Russian nouns, which adds a character which the phonology deletes, but which triggers various phonological rules.
